Circumpolar variations in the chaotic nature of Southern Ocean eddy dynamics

### 2022-01-09 paper/main.tex
Updating for Sally, Bill, Josue final comments

\authors{
Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez-Moreno\affil{1}
}

\affiliation{1}{Research School of Earth Sciences and ARC Centre of Excellence for Climate Extremes,\\ Australian National University, Canberra, Australia}
\affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, Institut des G{\'e}osciences de l'Environnement (IGE), Grenoble, France}
\affiliation{3}{Florida State University, Tallahassee, FL, USA}

@@

The heterogeneity in correlations between local wind and the ensemble mean EKE ($\langle E_i \rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
The existence of multi-year lags between the wind and the EKE suggests that local winds may not be the only source of energy for eddy generation; in particular, it is possible that energy could be advected a considerable distance downstream during this lag period.
To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}).
To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with ensemble mean EKE at different lags.
In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle E_i \rangle$ occurs within the EKE-averaging region.
This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing to the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKEaveraging region.
In the South Atlantic, the $\langle E_i \rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
Thus, these spatial maps demonstrate that, where strong forced variability in the ensemble mean EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.

@@

Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and the ensemble mean EKE: one at 4-6 months, and the other at $\sim$30 months.
The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
This mechanism the direct eddy response to wind stress changes via baroclinic instability.

@@

\acknowledgments
This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), which is supported by the Australian Government.
AMH is gratefully to the MEOM team at ICE, Universit{\'e} Grenoble Alpes, who supported his sabbatical and which led to this work. 
The results of this research have been achieved using the PRACE Research Infrastructure resource CURIE based in France at TGCC. 
This work is a contribution to the OCCIPUT and PIRATE projects. 
OCCIPUT has been funded by ANR through contract ANR-13-BS06-0007-01. 
PIRATE has been funded by CNES through the Ocean Surface Topography Science Team (OST-ST). 
{\color{red}The model output used in this study can be downloaded from the Zenodo repository at doi:XXX.XXX.XXX.}
The full OCCIPUT model dataset is available on request (\href{mailto:Thierry.Penduff@cnrs.fr}{Thierry.Penduff@cnrs.fr}).

>>>>

\authors{
Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2,4}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez-Moreno\affil{1,4}
}

\affiliation{1}{Research School of Earth Sciences and ARC Centre of Excellence for Climate Extremes,\\ Australian National University, Canberra, Australia}
\affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, Institut des G{\'e}osciences de l'Environnement (IGE), Grenoble, France}
\affiliation{3}{Florida State University, Tallahassee, FL, USA}
\affiliation{4}{Now at: Laboratoire d'Oc\'eanographie Physique et Spatiale (LOPS), University of Brest/IFREMER/IRD/CNRS, Brest, France}

@@

The heterogeneity in correlations between local wind and the ensemble mean EKE ($\langle E_i \rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
The existence of multi-year lags between the wind and the EKE suggests that local winds may not be the only source of energy for eddy generation; in particular, it is possible that energy could be advected a considerable distance downstream during this lag period.
To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}).
To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with ensemble mean EKE at different lags.
In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle E_i \rangle$ occurs within the EKE-averaging region.
This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing to the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKE-averaging region.
In the South Atlantic, the $\langle E_i \rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
Thus, these spatial maps demonstrate that, where strong forced variability in the ensemble mean EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.

@@

Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and the ensemble mean EKE: one at 4-6 months, and the other at $\sim$30 months.
The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
This mechanism is the direct eddy response to wind stress changes via baroclinic instability.

@@

\acknowledgments
This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), which is supported by the Australian Government.
AMH is gratefully to the MEOM team at ICE, Universit{\'e} Grenoble Alpes, who supported his sabbatical and which led to this work. 
The results of this research have been achieved using the PRACE Research Infrastructure resource CURIE based in France at TGCC. 
This work is a contribution to the OCCIPUT and PIRATE projects. 
OCCIPUT has been funded by ANR through contract ANR-13-BS06-0007-01. 
PIRATE has been funded by CNES through the Ocean Surface Topography Science Team (OST-ST). 
WKD was funded by ANR-18-MPGA-0002 and NSF grants oce-182956 and oce-2023585.
{\color{red}The model output used in this study can be downloaded from the Zenodo repository at doi:XXX.XXX.XXX.}
The full OCCIPUT model dataset is available on request (\href{mailto:Thierry.Penduff@cnrs.fr}{Thierry.Penduff@cnrs.fr}).
